First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-05-25 ms.tex
Updated caption to slice figure to mention RTS-CHIPS lines
Updated limit table for new CHIPS values

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{slices.pdf}
\caption{
\emph{Left:} The N-S, $z=6.8$ two dimensional power spectrum repeated from 
Figure~\ref{fig:2d_ps_subband}. Here we have superimposed blue lines to show slices in
$k_{\perp}$ (solid) and $k_{||}$ (dashed). \emph{Top right:} Residual power as a function
of $k_{\perp}$ for fixed $k_{||}$. The grey boxes show regions which will be excluded from
the one dimensional averages. The red dashed line shows the 1-$\sigma$ noise level, and
the vertical black dashed line shows the intersection of this slice with the wedge. 
\emph{Bottom right:} Residual power as a function of $k_{||}$ for fixed $k_{\perp}$. The strong
foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
appear as expected. 
\label{fig:slices}
}
\end{center}
\end{figure*}

@@

\begin{deluxetable}{ccccccc}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
\tablewidth{\columnwidth}
\tablecaption{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level. Cosmological wavenumbers, $k$, are in units of h~Mpc$^{-1}$ and upper limits are in units of mK$^2$. The last two columns, RTS-CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
\label{tbl:limits}
}
\tablehead{
& & & \multicolumn{2}{c}{FHD-\eppsilon} & \multicolumn{2}{c}{RTS-CHIPS} \\
Sub-band & $z_0$ & Pol & $k$  & $\Delta^2_{\text{UL}}$ & $k$ & $\Delta^2_{\text{UL}}$
}
\startdata
Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.15 & 4.0 $\times 10^4$ \\
Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.15 & 3.0 $\times 10^4$ \\
High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.15 & 3.2 $\times 10^4$ \\
\enddata
\end{deluxetable}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{slices.pdf}
\caption{
\emph{Left:} The N-S, $z=6.8$ two dimensional power spectrum repeated from 
Figure~\ref{fig:2d_ps_subband}. Here we have superimposed blue lines to show slices in
$k_{\perp}$ (solid) and $k_{||}$ (dashed). \emph{Top right:} Residual power as a function
of $k_{\perp}$ for fixed $k_{||}$. The grey boxes show regions which will be excluded from
the one dimensional averages. The red dashed line shows the 1-$\sigma$ noise level, and
the vertical black dashed line shows the intersection of this slice with the wedge. 
\emph{Bottom right:} Residual power as a function of $k_{||}$ for fixed $k_{\perp}$. The strong
foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
appear as expected. The thin black line in both right panels is the equivalent power slice from the RTS-CHIPS comparison pipeline, which is discussed in Section~\ref{subsec:ref_pipe}.
\label{fig:slices}
}
\end{center}
\end{figure*}

@@

\begin{deluxetable}{ccccccc}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
\tablewidth{\columnwidth}
\tablecaption{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level. Cosmological wavenumbers, $k$, are in units of h~Mpc$^{-1}$ and upper limits are in units of mK$^2$. The last two columns, RTS-CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
\label{tbl:limits}
}
\tablehead{
& & & \multicolumn{2}{c}{FHD-\eppsilon} & \multicolumn{2}{c}{RTS-CHIPS} \\
Sub-band & $z_0$ & Pol & $k$  & $\Delta^2_{\text{UL}}$ & $k$ & $\Delta^2_{\text{UL}}$
}
\startdata
Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.12 & 2.5 $\times 10^4$ \\
Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.14 & 2.2 $\times 10^4$ \\
High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.12 & 2.3 $\times 10^4$ \\
\enddata
\end{deluxetable}
